Manuscript 1 code

### 2025-01-28 manuscript_1_code.Rmd
further specified how to run model

# area model - play around with area vs. area_trans
area_mod <- glmmTMB(area ~ richness*habitat + (1|site/location) + (1|year), family = ziGamma("log"), ziformula = ~1, data = alpha_diversity_quad_macro)
summary(area_mod)
Anova(area_mod)
hist(residuals(area_mod))
plot(simulateResiduals(area_mod))
plot(residuals(area_mod) ~ fitted(area_mod)) # heteroskedastic - because of the few 100% cover plots?
r.squaredGLMM(area_mod) # 0.631, 0.650
performance::r2(area_mod) # 0.635, 0.654
emtrends(area_mod, pairwise ~ habitat, var = "richness")

>>>>

# area model - play around with area vs. area_trans. If you use area_trans, family = Gamma("log") and remove ziformula argument
area_mod <- glmmTMB(area ~ richness*habitat + (1|site/location) + (1|year), family = ziGamma("log"), ziformula = ~1, data = alpha_diversity_quad_macro)
summary(area_mod)
Anova(area_mod)
hist(residuals(area_mod))
plot(simulateResiduals(area_mod))
plot(residuals(area_mod) ~ fitted(area_mod)) # heteroskedastic - because of the few 100% cover plots?
r.squaredGLMM(area_mod) # 0.631, 0.650
performance::r2(area_mod) # 0.635, 0.654
emtrends(area_mod, pairwise ~ habitat, var = "richness")
